Judging domestic cooking ability: repeated incomplete rank observations

### 2022-12-22 inst/cook_repeated.Rmd
use sticker in Rmd
consider ordertable2supp() [it is not correct]

Suppose there are five people in a family.  Each day for five days,
one person cooks a meal.  After the fifth day, each person considers
the four meals cooked by other family members, and puts them in order
of preference.  This process is repeated and here I consider how to
interpret such data.

@@

```{r}
(day1 <- cooking_table[1,])
H_row1 <- rank_likelihood(day1[day1>0])
```

@@

```{r}
p <- c(0.3,0.2,0.1,0.3)
# Now create p2 which is the same but competitor 1 is stronger:
p2 <- p
alpha <- 1.3
beta <- (1-alpha*p[1])/(1-p[1])
p2[1] <- p2[1]*alpha   # person 1 becomes stronger...
p2[-1] <- p2[-1]*beta  # ...and everyone else becomes weaker

@@

```{r}
H <- hyper2()

@@

@@

```{r}
equalp.test(H)
mH <- maxp(H)
mH
pie(mH)
```

@@

```{r}
a <- cooking_table # saves typing
a <- a[a[,4]>0,]  # just lines where zac does not vote
jj <- table(robin_votes=a[,1]==0,zac_last=a[,4]==4)
jj
```

@@

```{r}
fisher.test(jj,alternative="less")
```

@@

```{r}
a <- cooking_table # saves typing
a <- a[a[,1]>0,]  # just lines where robin does not vote
jj <- table(zac_votes=a[,4]==0,robin_last=a[,1]==4)
jj
fisher.test(jj,alternative="less")
```

@@

```{r,cache=TRUE}
cooking_table <-
	as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table <- cooking_table[rowSums(cooking_table==0)==1,]
boys <-c("robin","zac")
girls <- c("lesley","alice","annabel")
cooks <- colnames(cooking_table)
P <- hyper2()
P0 <- hyper2()
for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
	if(sum(x==0)>1){break}
    names(x) <- cooks
	if(names(x[x==0]) %in% boys){  # if the voter is a boy
		x <- x[x>0]  # remove the voter
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% boys], chameleon="boy")
	} else if (names(x[x==0]) %in% girls){ # voter a girl
		x <- x[x>0]
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% girls], chameleon="girl")
	} else {
		stop()
	}
    P <- P + Pjj
}
mP <- maxp(P)
```

```{r}
mP
pie(mP)
```

@@

```{r,cache=TRUE}
specificp.gt.test(P,"girl",0)
```

>>>>

<p style="text-align: right;">
![](`r system.file("help/figures/hyper2.png", package = "hyper2")`){width=10%}
</p>

(takes about five minutes without cache).
Suppose there are five people in a family.  Each day for five days,
one person cooks a meal.  After the fifth day, each person considers
the four meals cooked by other family members, and puts them in order
of preference.  This process is repeated and here I consider how to
interpret such data.

@@

```{r lookatfirstrow}
(day1 <- cooking_table[1,])
H_row1 <- rank_likelihood(day1[day1>0])
```

@@

```{r uninformativeaboutcomp1}
p <- c(0.3,0.2,0.1,0.3)
# Now create p2 which is the same but competitor 1 is stronger:
p2 <- p
alpha <- 1.3
beta <- (1-alpha*p[1])/(1-p[1])
p2[1] <- p2[1]*alpha   # person 1 becomes stronger...
p2[-1] <- p2[-1]*beta  # ...and everyone else becomes weaker

@@

```{r iterateoverrows,cache=TRUE}
H <- hyper2()

@@

*NOTE*: converting `cooking_table` to an order table is _not_ correct,
for the zero is interpreted as "did not finish", but the correct
interpretation is "did not take part": the difference is that DNF
implies lower trength, but the likelihood function is uninformative
about DNTP players.  Even so, we may use `ordertable2supp()`:

```{r showtrahnsposeisanordertable,cache=TRUE}
tc <- t(cooking_table)
tc[,1:20]
```

@@

```{r equalptest,cache=TRUE}
equalp.test(H)
mH <- maxp(H)
mH
pie(mH)
```

@@

```{r trysimplethings}
a <- cooking_table # saves typing
a <- a[a[,4]>0,]  # just lines where zac does not vote
jj <- table(robin_votes=a[,1]==0,zac_last=a[,4]==4)
jj
```

@@

```{r tryfishertest}
fisher.test(jj,alternative="less")
```

@@

```{r tryfishertestzac}
a <- cooking_table # saves typing
a <- a[a[,1]>0,]  # just lines where robin does not vote
jj <- table(zac_votes=a[,4]==0,robin_last=a[,1]==4)
jj
fisher.test(jj,alternative="less")
```

@@

```{r girlsvotinggirls,cache=TRUE}
cooking_table <-
	as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table <- cooking_table[rowSums(cooking_table==0)==1,]
boys <-c("robin","zac")
girls <- c("lesley","alice","annabel")
cooks <- colnames(cooking_table)
P <- hyper2()
P0 <- hyper2()
for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
	if(sum(x==0)>1){break}
    names(x) <- cooks
	if(names(x[x==0]) %in% boys){  # if the voter is a boy
		x <- x[x>0]  # remove the voter
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% boys], chameleon="boy")
	} else if (names(x[x==0]) %in% girls){ # voter a girl
		x <- x[x>0]
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% girls], chameleon="girl")
	} else {
		stop()
	}
    P <- P + Pjj
}
mP <- maxp(P)
```

```{r plotapie}
mP
pie(mP)
```

@@

```{r girlspref, cache=TRUE}
specificp.gt.test(P,"girl",0)
```
